\section{conclusion}
\label{sec:conclusion}
We presented \imss, a solver for string constraints. \imss is the integration of
multiple solvers. More specifically, \hampi, \dprle and \zstr. The inputs to \imss can express
membership and string functions such as replace, length, contains and substring. The constraints
can contain arbitrary string variables, context-free language definitions, integers,
and regular language definitions. Given string constraints, \imss outputs
a string that satisfies the constraints, or reports that the constraints are incompatible with the list of supported solvers of \imss.
As long as one of \imss's solvers can solve the constraints, users do not have to decide which solver
they should use to solve their constraints.

We evaluated \imss on \pickedtests tests. These tests are known to contain all of the functionalities
tests of the three solvers check for. Our experiments shows that \imss can solve all of the tests
with no noticeable overhead.

\dprle is the fastest solver, but it lacks many of the functionalities other solvers have. \zstr can solve
the greatest number of string constraints without context-free grammar definitions. For constraints with context-free grammer, \hampi is the only solver capable of solving such constraints.

Due to the time limit we had to complete the implementation, evaluation and write up for \imss, multiple tasks were planned but delayed.
In the future, we plan to improve \imss in the following ways:
\begin{enumerate}
    \item For the solvers that \imss supports, we would like the feature to translate constraints written in such solver's language to \imss's language.
    \item We plan to accept SMT-LIB's format as input so that all solvers that support SMT-LIB can be used by \imss.
    \item We plan to add other constraints solvers that do not support SMT-LIB such as Kaluza~\cite{kaluza2010} to \imss.
    \item We plan to use a constraint generator to provide additional test cases to better understand the strengths and weakness of the solvers supported by \imss.
\end{enumerate}
