\section{related works}
\label{sec:related}

Boolector is an efficient SMT solver for the quantifier-free theory
of bit-vectors in combination with the extensional theory of arrays~\cite{boolector2009}.
Boolector depends on term rewriting and bit-blasting for bit-vectors. It
takes a formula expressed in the SMT-LIB format~\cite{smtlib2015}, or alternatively in
the BTOR format~\cite{btor2008}, as input.
The BTOR format is a low-level bit-vector format with clean semantics that is easy to
parse. Additionally, BTOR supports bit-vector arrays and model checking of safety
properties.
Aside from being an SMT solver, Boolector contains a tool known as
Pretty Printer. Pretty Printer allows Boolector to convert formulas from BTOR to
SMT-LIB format and vice versa. The Pretty Printer can be combined with Boolector’s
rewriting module to internally simplify the formula before conversion.
Pretty Printer is the only existing tool (to the best of our knowledge) that is capable of
converting from one language format to another for constraint solving purposes.
While Pretty Printer can convert between 2 languages, \imss is able to convert
between 4 different languages with many more planned to be added soon.

SMT-LIB is an international initiative aimed at facilitating research and development in
Satisfiability Modulo Theories (SMT)~\cite{smtlib2015}. Since its inception in 2003, the
initiative has focused on 5 concrete goals. One of these goals is to develop and promote
common input and output languages for SMT solvers.
SMT-LIB has accomplished this by providing a way for developers of constraint solvers
to integrate SMT-LIB with their solvers.
Compared to \imss, \imss does not require developers of constraint solver to
do anything and it alleviates the burden users have in
determining which solver is best at solving particular constraints.
